PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected missingness chunks, added item cut offs and sum score cut offs

>>>>

#Sum scores missingness cut offs
KT: This series of chunks creates a "full" sum score for the PHQ, GAD and PCL.

PHQ
The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.base_cut_off)
```{r sum score cut offs PHQ base}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.sum_score_base_full =
      if_else(na_per_person_phq_base > 1 & phq.base_cut_off == 0,
              NA_real_,
              phq.sum_score_base
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base)
summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base_full)
```

```{r sum score cut offs PHQ prepan}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.sum_score_prepan_full =
      if_else(na_per_person_phq_prepan > 1 & phq.prepan_cut_off == 0,
              NA_real_,
              phq.sum_score_prepan
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan)
summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan_full)
```

```{r sum score cut offs PHQ retro}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.sum_score_retro_full =
      if_else(na_per_person_phq_retro > 1 & phq.retro_cut_off == 0,
              NA_real_,
              phq.sum_score_retro
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro)
summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro_full)
```

GAD
The GAD sum score is set to NA if they have any missing items
```{r sum score cut offs GAD base}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    gad.sum_score_base_full =
      if_else(na_per_person_gad_base > 0,
              NA_real_,
              gad.sum_score_base
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base)
summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base_full)
```

```{r sum score cut offs GAD prepan}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    gad.sum_score_prepan_full =
      if_else(na_per_person_gad_prepan > 0,
              NA_real_,
              gad.sum_score_prepan
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan)
summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan_full)
```

```{r sum score cut offs GAD retro}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    gad.sum_score_retro_full =
      if_else(na_per_person_gad_retro > 0,
              NA_real_,
              gad.sum_score_retro
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro)
summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro_full)
```

PCL
The PCL sum score is set to NA if they have any missing items - only for basline and prepan.
```{r sum score cut offs PCL base}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    pcl.sum_score_base_full =
      if_else(na_per_person_pcl_base > 0,
              NA_real_,
              pcl.sum_score_base
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base)
summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base_full)
```

```{r sum score cut offs PCL prepan}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    pcl.sum_score_prepan_full =
      if_else(na_per_person_pcl_prepan > 0,
              NA_real_,
              pcl.sum_score_prepan
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan)
summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan_full)
```
